First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-08-05 ms.tex
Couple of minor wording tweaks from JDB

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{example_2derror.pdf}
\caption{
\textbf{
Error level corresponding to Figure~\ref{fig:example_ps}. The noise is relatively low at
short baseline length (low $k_{\perp}$) due to the dense MWA core. The array is more
sparse at longer baselines, and the noise increases. The second $k_{||}$ bin has slightly
lower noise than the rest of the $k_{||}$ modes due to the interaction between the
Lomb-Scargle periodogram with the Blackman-Harris window function applied to the data.
}
\label{fig:example_2derror}
}
\end{center}
\end{figure}

\textbf{Figure~\ref{fig:example_2derror} shows the error level corresponding to the two 
dimensional power spectrum in Figure~\ref{fig:example_ps}. These errors
are found by propagating noise measured from calibrated visibilities through the entire
pipeline. The dense core of the MWA results in relatively low noise at low $k_\perp$.
As the $(u,v)$ density of the array decreases at longer baselines, the noise increases.
The noise is mostly constant across $k_{||}$ because the Fourier transform distributes
the noise in frequency to all modes equally \citep{Morales:2004}.
The exception is the second $k_{||}$ bin, which has slightly lower noise than the rest of the 
$k_{||}$ modes. 
As explained in Hazelton et al. (in prep.) this is a result of the Lomb-Scargle periodogram 
interacting with the Blackman-Harris window function we apply to the data. Most of the bins 
have the noise equally distributed between cosine and sine terms, with the exception of the 
$k_{||}=0$ bin where the cosine term carries all the information. Due to the correlations 
introduced by the Blackman-Harris window function the first non-zero $k_{||}$ mode is highly 
covariant with the bottom bin -- therefore the noise on this mode's cosine term is lower than 
other higher order cosines.
}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{example_2derror.pdf}
\caption{
\textbf{
Uncertainty level corresponding to Figure~\ref{fig:example_ps}. The noise is relatively low at
short baseline length (low $k_{\perp}$) due to the dense MWA core. The array is more
sparse at longer baselines, and the noise increases. The second $k_{||}$ bin has slightly
lower noise than the rest of the $k_{||}$ modes due to the interaction between the
Lomb-Scargle periodogram with the Blackman-Harris window function applied to the data.
}
\label{fig:example_2derror}
}
\end{center}
\end{figure}

\textbf{Figure~\ref{fig:example_2derror} shows the uncertainty level corresponding to the two 
dimensional power spectrum in Figure~\ref{fig:example_ps}. These levels
are found by propagating noise measured from calibrated visibilities through the entire
pipeline. The dense core of the MWA results in relatively low noise at low $k_\perp$.
As the $(u,v)$ density of the array decreases at longer baselines, the noise increases.
The noise is mostly constant across $k_{||}$ because the thermal noise amplitude is
relatively constant over frequency and the Fourier transform distributes the noise power
across all modes \citep{Morales:2004}.
The exception is the second $k_{||}$ bin, which has slightly lower noise than the rest of the 
$k_{||}$ modes. 
As explained in Hazelton et al. (in prep.) this is a result of the Lomb-Scargle periodogram 
interacting with the Blackman-Harris window function we apply to the data. Most of the bins 
have the noise equally distributed between cosine and sine terms, with the exception of the 
$k_{||}=0$ bin where the cosine term carries all the information. Due to the correlations 
introduced by the Blackman-Harris window function the first non-zero $k_{||}$ mode is highly 
covariant with the bottom bin -- therefore the noise on this mode's cosine term is lower than 
other higher order cosines.
}
